Functions Created

### 2017-08-25 Hours.Rmd
updated hours
update hours

>>>>

8/23/2017 | 9.5 | 9:00-6:30 | More spline research, cross-validated on models with different splines, compared models, fit final model(?)
8/23/2017 | 1 | 7:45-8:45PM | Plotted residuals, assessed PH assumption, researched effect of violation of PH assumption 
8/24/2017 | 2 | 10:00-12:00AM | Read Regression Modeling Strategies text book
8/24/2017 | 3.5 | 3:00-6:30PM | Continued reading regression modeling strategies book + other literature, tried to apply it to the data
8/24/2017 | 1.5 | 7:30-9:00PM | Residuals, checked PH assumption, tried to address PH assumption violations
